---
title: "Untitled"
author: "aa"
date: "21 8 2020"
output: 
  html_document:
    css: "styles.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages:

```{r warning=FALSE, include=FALSE}
## Libraries
library(tidyverse)
library(survival)
library(survminer)
library(ggplot2)
library(ggfortify)
```


```{r warning=FALSE}
## Data manipulation 

## Set working directory 
dir <- "C:/Users/anssi/Desktop/Ohjelmointi/R_Projektit/occupational_health"
setwd(dir)

## Load the csv files
data_raw <- read.csv("data/2017-05-29-tyojaterveys-opendata-COMPLETE.csv", sep = "")
meta_raw <- read.csv("data/2017-05-29-tyojaterveys-metadata-LARGE.csv", sep = "")

## Metadata transformation
meta <- meta_raw %>% 
  select(questionID, columnNameLong, codeKey) %>% 
  na.omit() 

meta <- meta %>% 
  separate(codeKey, sep = ",", into = paste0("codeKey", seq_len(max(str_count(meta$codeKey, ",")) + 1))) %>% 
  gather(key = "codeKey", value = "answer", -questionID, -columnNameLong) %>% 
  separate(answer, sep = "=", into = c("answer", "descr")) %>% 
  select(-codeKey)

## Data transformation
data <- data_raw %>% 
  gather(key = "questionID", value = "answer", -id, -vuosi)

## Join with actual data with metadata
data <- left_join(data,  meta %>% select(questionID, columnNameLong), by = c("questionID" = "questionID")) %>% 
  distinct() %>% 
  na.omit()

data <- left_join(data, meta %>% select(questionID, answer, descr), by = c("questionID" = "questionID", "answer" = "answer"))

## Some of the answer need to be edited manually
data$descr <- ifelse(data$questionID == "t11", data$answer, data$descr)
data$descr <- ifelse(data$questionID == "tol2008", data$answer, data$descr)

## Last NA -value omit
data <- na.omit(data)

## Rename variables
colnames(data) <- c("person_id", "year", "question_id", "answer_id", "question", "answer")
```

Because we are interested on the age of the respondent we need to edit it to proper format.

The difficulty of the age lies in the way the response is given. The respondent can answer his/her age to be somewhere between 35-44 depending on the age group.
To perform proper survival analysis on the data, we need the age to be numerical variable. The solution to this problem is to simulate the respondents age.
First we start by creating a simulation function. Round(runif(min, max)) combination returns a discrete uniform distribution across the min and max values. 

```{r}
## Age simulation function
age_simulation <- function(x){
  if(x == "1"){
    round(runif(1, min = 24, max = 34), digits = 1)
  } else if(x == "2") {
    round(runif(1, min = 34, max = 44), digits = 1)
  } else if(x == "3") {
    round(runif(1, min = 44, max = 54), digits = 1)
  } else {
    round(runif(1, min = 54, max = 64), digits = 1)
  }
}
```

To test if the simulation works as it should, we want to see the distribution of the age groups and the numerical age values.

The first plots shows us the actual distribution of the age groups.

```{r}
## Age group plot 

```


```{r}
## Filter the data
data <- data %>% 
  select(person_id, year, question_id, answer, age_simulated) %>% 
  filter(question_id %in% c("tol2008", "b1", "f2", "ika", "t11")) %>% 
  mutate(answer = ifelse(question_id == "ika", age_simulated, answer)) %>% 
  select(-age_simulated)
```


